GVN-Hoist: Hoisting Computations from Branches

### 2016-08-24 hoist.tex
remove Dan Berlin from authors
abstract

\maketitle
\begin{abstract}
  Code-hoisting identifies identical computations across the program with the
  help of a Global Value Numbering (GVN) analysis, identifies a hoisting
  position that dominates all the identical computations and in which all
  operands are avaialable, duplicates one of the expressions in the hoisting
  position, and removes all the computations now redundant in their original
  position.

  Code-hoisting is often confused with CSE (Common Subexpression Elimination)
  although code-hoisting is not bound to find redundancies within a single basic
  block.  Code-hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or with Global Common Subexpression Elimination (GCSE)
  although the main goal of code-hoisting is not to remove redundancies:
  code-hoisting effectively exposes redundancies and enables other passes like
  LICM to remove more redundancies.  The main goal of code-hoisting is to reduce
  code size with the added benefit of exposing more instruction level
  parallelism and reduced register pressure.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
  Code-hoisting identifies identical computations across the program and hoists
  them to a common dominator so as to save code size.  Although the main goal of
  code-hoisting is not to remove redundancies: it effectively exposes
  redundancies and enables other passes like LICM to remove more redundancies.
  The main goal of code-hoisting is to reduce code size with the added benefit
  of exposing more instruction level parallelism and reduced register pressure.

  We present a code hoisting pass that we implemented in llvm. It is based on
  Global Value Numbering infrastructure available in llvm. The experimental
  results show an average of 2.5\% savings in code size, although the code size
  increases in many cases because it enables more inlining. This is an
  optimistic algorithm in the sense that we consider all identical computations
  in a function as potential candidates to be hoisted. We make an extra effort
  to hoist candidates by partitioning the potential candidates in a way to
  enable partial hoisting in case common hoisting points for all the candidates
  cannot be found. We also formalize cases when register pressure will reduce as
  a result of hoisting.
\end{abstract}
